Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-10 draft.tex
work on 8.2

Our work here relies on a concrete and convenient model for these enveloping $\EE_n$ algebras by factorization algebras.
In particular, thanks again to \cite{Knudsen}, 
we know that the $\EE_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
There is another factorization algebra whose underlying assigns $\clies(\Omega^\bu(V) \otimes \fg)$ to each open~$V$.
Our paper shows that such factorization algebras model other important $\EE_n$ algebras, notably centralizers.

@@

\begin{qtn}
Is there some local version of this relationship? That is, can we obtain a version of the LQT theorem at the level of $\EE_n$ algebras such that factorization homology recovers the quasi-isomorphism of this lemma?
\end{qtn}

@@

In this section, we turn to an interpretation of the $\EE_n$ center of an $\EE_n$ enveloping algebra in terms of a certain topological field theory (TFT).

Given an $\EE_n$ algebra $A$, the pair $(\fZ_n (A) , A)$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
The first objective is to define a certain ``classical limit" of this pair in the case that $A$ is an $\EE_n$ enveloping algebra.

@@

The key insight is that there exists a filtration on our model $\bZ_n(\fg)$ for the $\EE_n$ center and our model $\bU_n (\fg)$ for the $\EE_n$ enveloping algebra  whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.

@@

Consider our factorization model for the $\EE_n$ enveloping algebra $\bU_n(\fg) = \cliels (\fg \otimes \Omega^\bu_c)$. 
The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.

@@

\begin{proof}
For any $L_\infty$ algebra $\fh$, the associated graded of the Chevalley--Eilenberg complex ${\rm Gr} \; \cliels {\rm Sym} (\fh [1])$ is equipped with the structure of a $\PP_0$ algebra.
It is given by the sum of the $L_\infty$-operations $\ell_2 + \ell_3 + \cdots$. 
This implies that ${\rm Gr} \; \bU_n (\fg)$ is a $\PP_0$-factorization algebra.

@@

The pair $(\fZ_n(\fg), \UU_n(\fg))$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
At the level of the associated graded algebras, we obtain an algebra over a certain classical limit of this operad which takes into account the aforementioned Poisson structures.

The definition of this two-colored operad $\PP_{[n+1,n]}$ can be found in \cite{SafronovCoiso}. 
A $\PP_{[n+1,n]}$ algebra consists of a pair $(A,B)$ where $A$ is a $\PP_{n+1}$ algebra and $B$ is a $\PP_n$ algebra which receives an action by $A$.

The action of $\bZ_n(\fg)$ on $\bU_n(\fg)$ descends to an action at the level of the associated graded factorization algebras
Together with Lemma \ref{lmm:pois1}, we obtain Proposition \ref{prp:poisson}.

@@

We turn towards a model for the $\EE_n$-center as a constructible factorization algebra on an $(n+1)$-manifold with boundary.

@@

\begin{rmk}
For an open $U \subset M \times \RR_{>0}$, pulling back along an embedding $\iota : U \hookrightarrow V \times [0,\epsilon)$ determines a composition of cochain complexes
\[
\Omega^\bu (V') \otimes \Tilde{\Omega}^\bu([0,\epsilon)) \xto{j^*}  \Omega^\bu (V') \Hat{\otimes} \Omega^\bu((0,\epsilon)) \cong \Omega^\bu(V \times (0,\epsilon)) \xto{\iota^*} \Omega^\bu(U) .
\]
This is our model for restriction $\iota^*$ of de Rham forms that is used in the definition above.
\end{rmk}

@@

\begin{proof}[Proof of Proposition \ref{prp:pair}]
To exhibit this quasi-isomorphism, we introduce the following cochain maps.
For an open set $V \subset M$ let
\[
\int_{\RR_{>0}} : \Omega_c(V \times \RR_{>0}) \to \Omega_c (U) [1] 
\] 
be the map which integrates a compactly supported form on $U \times \RR_{> 0}$ along $\RR_{> 0}$. 
This map is a quasi-isomorphism for any $U$ and, in fact, admits the following explicit retract. 
Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
\[
r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR_{\geq 0})
\]
by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$.

Notice that for an open set $V \subset M$ we have 
\[
\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega (V \times \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega_c(V \times \RR_{>0}) [2] \right) \bigg)  .
\]
Integration along $\RR_{>0}$ induces a map of factorization algebras on $M$
\[
I^{\circ} : \bC_n(\fg)^\circ \to {\rm Gr} \; \bZ_n (\fg)
\]
which on linear elements in ${\rm Sym}(\fg \otimes \Omega^\bu_c (V \times \RR_{>0})$ sends $x \otimes \alpha \in \Omega^\bu_c(V \times \RR_{>0})[2]$ to $x \otimes \int_{\RR_{>0}} \alpha \in \Omega^\bu_c (V)[1]$.

Next, using the map $r_\phi$, wedefine a map of factorization algebras
\[
r_\phi^\circ : {\rm Gr} \; \bZ_n (\fg) \to \bC_n(\fg)^\circ
\]
as follows. 
For an open set $V \subset M$, define $r_{\phi}^\circ (V)$ on linear elements $x \otimes \alpha$ in $\Sym(\fg \otimes \Omega^\bu(V)_c[1])$ by
\[
r_\phi^\circ (U) (x \otimes \alpha) = x \otimes (\pi^* \alpha \wedge \phi \d t)  .
\]
This map can be extended to all of ${\rm Gr} \; \bZ_n(\fg)$ in a similar fashion. 
One can show that $r_\phi^\circ$ is a deformation retract of $I^\partial$.
In particular, $I^\partial$ is a quasi-isomorphism of factorization algebras on $M$.

Similarly, integration of compactly supported forms along $\RR_{\geq 0}$ determines a quasi-isomorphism of factorization algebras 
\[
I^\partial : \bC_n(\fg)^\partial \to {\rm Gr} \; \bU_n(\fg) .
\]
Recall that for $V \subset M$ we have
\[
\bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) .
\]
On $V$, the map $I^\partial (V)$ is defined by the composition
\[
\begin{tikzcd}
\clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \otimes \Omega^\bu_c (V)[1] \right) .
\end{tikzcd}
\]
The first map ${\rm ev}_1$ evaluates the unit in $\Sym \left(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})\right)$ and the second map is induced by integration along $\RR_{\geq 0}$. 
It is quick to check that $I^{\partial}$ extends to a map of factorization algebras.

>>>>

Our work here relies on a concrete and convenient model for these enveloping $\EE_n$ algebras by factorization algebras.
In particular, thanks again to \cite{Knudsen}, 
we know that the enveloping $\EE_n$ algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
There is another factorization algebra whose underlying assigns $\clies(\Omega^\bu(V) \otimes \fg)$ to each open~$V$.
Our paper shows that such factorization algebras model other important $\EE_n$ algebras, notably centralizers.

@@

\begin{qtn}
Is there a local version of this relationship? That is, can we obtain a version of the LQT theorem at the level of $\EE_n$ algebras such that factorization homology recovers the quasi-isomorphism of this lemma?
\end{qtn}

@@

In this section, we turn to an interpretation of the $\EE_n$ center of an enveloping $\EE_n$ algebra in terms of a certain topological field theory (TFT).

Given an $\EE_n$ algebra $A$, the pair $(\fZ_n (A) , A)$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
The first objective is to define a certain ``classical limit" of this pair in the case that $A$ is an enveloping $\EE_n$ algebra.

@@

The key insight is that there exists a filtration on our model $\bZ_n(\fg)$ for the $\EE_n$ center and our model $\bU_n (\fg)$ for the enveloping $\EE_n$ algebra  whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.

@@

Consider our factorization model for the enveloping $\EE_n$ algebra $\bU_n(\fg) = \cliels (\fg \otimes \Omega^\bu_c)$. 
The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.

@@

\begin{proof}
For any $L_\infty$ algebra $\fh$, the associated graded of the Chevalley--Eilenberg complex ${\rm Gr} \; \cliels {\rm Sym} (\fh [1])$ is equipped with the structure of a $\PP_0$ algebra.
It is given by the sum of the $L_\infty$-operations $\ell_2 + \ell_3 + \cdots$. 
This observation implies that ${\rm Gr} \; \bU_n (\fg)$ is a $\PP_0$-factorization algebra.

@@

The pair $(\fZ_n(\fg), \UU_n(\fg))$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
At the level of the associated graded algebras, 
we obtain an algebra over a certain classical limit of this operad that takes into account the aforementioned Poisson structures.
The definition of this two-colored operad $\PP_{[n+1,n]}$ can be found in~\cite{SafronovCoiso}. 
A {\em $\PP_{[n+1,n]}$ algebra} consists of a pair $(A,B)$ where $A$ is a $\PP_{n+1}$ algebra and $B$ is a $\PP_n$ algebra that receives an action by $A$.

The action of $\bZ_n(\fg)$ on $\bU_n(\fg)$ descends to an action at the level of the associated graded factorization algebras
Together with Lemma~\ref{lmm:pois1}, we obtain Proposition~\ref{prp:poisson}.

@@

We turn towards a model for the $\EE_n$ center as a constructible factorization algebra on an $(n+1)$-manifold with boundary.

@@

\begin{rmk}
For an open $U \subset M \times \RR_{>0}$, pulling back along an embedding $\iota : U \hookrightarrow V \times [0,\epsilon)$ determines a composition of cochain complexes
\[
\Omega^\bu (V') \otimes \Tilde{\Omega}^\bu([0,\epsilon)) \xto{j^*}  \Omega^\bu (V') \Hat{\otimes} \Omega^\bu((0,\epsilon)) \cong \Omega^\bu(V \times (0,\epsilon)) \xto{\iota^*} \Omega^\bu(U) .
\]
This composition provides the version of restriction $\iota^*$ of de Rham forms used in the definition above.
\end{rmk}

@@

\begin{proof}[Proof of Proposition \ref{prp:pair}]
To exhibit the desired quasi-isomorphism, 
we first construct a map of factorization algebras and then provide a retract that shows it is a quasi-isomorphism.

We will use the following cochain maps in our constructions.
For an open set $V \subset M$ let
\[
\int_{\RR_{>0}} : \Omega^*_c(V \times \RR_{>0}) \to \Omega^*_c (U) [1] 
\] 
be the map which integrates a compactly supported form on $U \times \RR_{> 0}$ along $\RR_{> 0}$. 
This map is a quasi-isomorphism for any $U$ and, in fact, admits the following explicit retract. 
Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
\[
r_\phi : \Omega^*_c(U) [1] \to \Omega^*_c (U \times \RR_{\geq 0})
\]
by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$.

Notice that for an open set $V \subset M$ we have 
\[
\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega^* (V \times \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega^*_c(V \times \RR_{>0}) [2] \right) \bigg)  .
\]
Integration along $\RR_{>0}$ induces a map of factorization algebras on $M$
\[
I^{\circ} : \bC_n(\fg)^\circ \to {\rm Gr} \; \bZ_n (\fg)
\]
that on linear elements in ${\rm Sym}(\fg \otimes \Omega^\bu_c (V \times \RR_{>0}))$ sends $x \otimes \alpha \in \fg \otimes \Omega^\bu_c(V \times \RR_{>0})[2]$ to $x \otimes \int_{\RR_{>0}} \alpha \in \fg \otimes \Omega^\bu_c (V)[1]$.

Next, using the map $r_\phi$, we define a map of factorization algebras
\[
r_\phi^\circ : {\rm Gr} \; \bZ_n (\fg) \to \bC_n(\fg)^\circ
\]
as follows. 
For an open set $V \subset M$, define $r_{\phi}^\circ (V)$ on linear elements $x \otimes \alpha$ in $\Sym(\fg \otimes \Omega^\bu(V)_c[1])$ by
\[
r_\phi^\circ (U) (x \otimes \alpha) = x \otimes (\pi^* \alpha \wedge \phi \d t)  .
\]
This map can be extended to all of ${\rm Gr} \; \bZ_n(\fg)$ in a similar fashion. 
A quick computation shows that $r_\phi^\circ$ is a deformation retract of $I^\circ$.
In consequence, $I^\circ$ is a quasi-isomorphism of factorization algebras on~$M$.

Similarly, we now use integration of compactly supported forms along $\RR_{\geq 0}$ to produce  a quasi-isomorphism of factorization algebras 
\[
I^\partial : \bC_n(\fg)^\partial \to {\rm Gr} \; \bU_n(\fg) .
\]
We begin by constructing this map and then provide a retract that shows it is a quasi-isomorphism.

Recall that for $V \subset M$ we have
\[
\bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) .
\]
On $V$, the map $I^\partial (V)$ is defined by the composition
\[
\begin{tikzcd}
\clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \otimes \Omega^\bu_c (V)[1] \right) .
\end{tikzcd}
\]
The first map ${\rm ev}_1$ evaluates the unit in $\Sym \left(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})\right)$ and the second map is induced by integration along $\RR_{\geq 0}$. 
It is quick to check that $I^{\partial}$ extends to a map of factorization algebras.
